---
title: "GA"
author: "Sakana"
date: "11/3/2018"
output: html_document
---


Ref: Generalized Simulated Annealing for Global Optimization: The GenSA Package
An Application to Non-Convex Optimization in Finance and Physics
by Yang Xiang, Sylvain Gubian, Brian Suomela and Julia Hoeng

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Libraries

```{r}
library(GenSA)
library(ggplot2)
library(GA)
library(knitr)
library(kableExtra)
```

### SOLVING USING GENETIC ALGORITHM



#### PORTFOLIO OPTIMIZATION USING GA

```{r}
library("quantmod")
### defining tickers
tickers <- c("KO", "MS", "HPQ", "TM", "PEP")
getSymbols(tickers, from = "2000-12-01", to = "2018-11-02")
P <- NULL
for(ticker in tickers) {
  
###saving data of tickers in temp
  
 tmp <- Cl(to.monthly(eval(parse(text = ticker)))) 
 P <- cbind(P, tmp)
}
colnames(P) <- tickers
R <- diff(log(P))
R <- R[-1,]
mu <- colMeans(R)
sigma <- cov(R)
library("PerformanceAnalytics")
pContribCVaR <- ES(weights = rep(0.2, 5), method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)$pct_contrib_ES
obj <- function(w) {
 fn.call <<- fn.call + 1
 if (sum(w) == 0) { w <- w + 1e-2 }
 w <- w / sum(w)
 CVaR <- ES(weights = w, method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)
 tmp1 <- CVaR$ES
 tmp2 <- min(CVaR$pct_contrib_ES - 0.225, 0)
 out <- tmp1 + 1e3 * tmp2
 return(out)
}
```
#### Using Rastrigin function  

```{r}
Rastrigin <- function(x1, x2)
{
  20 + x1^2 + x2^2 - 10*(cos(2*pi*x1) + cos(2*pi*x2))
}
x1 <- x2 <- seq(-5.12, 5.12, by = 0.1)
f <- outer(x1, x2, Rastrigin)
```


### SOLVING FOR PERFORMANCE VALUES

```{r}
set.seed(1600)
fn.call <<- 0
fn.call.GenSA <- fn.call
genpro <- ga(type = "real-valued",fitness=function(w)-Rastrigin(w[1],w[2]),lower=rep(0,5),upper=rep(1,5), popSize = 1,maxiter = 150)
summary(genpro)
plot(genpro)
### calling the function
fn.call.GenSA <- fn.call
```

### SOLVING USING SIMULATION ALGORITHM

```{r}
library("quantmod")
tickers <- c("KO", "MS", "HPQ", "TM", "PEP")
getSymbols(tickers, from = "2000-12-01", to = "2018-11-02")
P <- NULL
for(ticker in tickers) {
 tmp <- Cl(to.monthly(eval(parse(text = ticker))))
 P <- cbind(P, tmp)
}
colnames(P) <- tickers
R <- diff(log(P))
R <- R[-1,]
mu <- colMeans(R)
sigma <- cov(R)
library("PerformanceAnalytics")
pContribCVaR <- ES(weights = rep(0.2, 5), method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)$pct_contrib_ES
obj <- function(w) {
 fn.call <<- fn.call + 1
 if (sum(w) == 0) { w <- w + 1e-2 }
 w <- w / sum(w)
 CVaR <- ES(weights = w, method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)
 tmp1 <- CVaR$ES
 tmp2 <- max(CVaR$pct_contrib_ES - 0.225, 0)
 out <- tmp1 + 1e3 * tmp2
 return(out)
}
```

```{r}
set.seed(1234)
fn.call <<- 0
out.GenSA <- GenSA(fn = obj, lower = rep(0, 5), upper = rep(1, 5), control = list(smooth = FALSE, max.call = 3000))
out.GenSA[c("value","par","counts")]
fn.call.GenSA <- fn.call
out.GenSA$value
out.GenSA$counts
cat("GenSA call functions", fn.call.GenSA, "times.\n")
wstar.GenSA <- out.GenSA$par
wstar.GenSA <- wstar.GenSA / sum(wstar.GenSA)
rbind(tickers, round(100 * wstar.GenSA, 2))
100 * (sum(wstar.GenSA * mu) - mean(mu))
wstar.GenSA
### comparing the values of GA and SA, in TABLE
TICKER_NAMES <- c('KO', 'MS', 'HPQ', 'TM', 'PEP')
VALUES_GA<- c(0.2325183, 0.6032943, 0.4259968, 0.645123, 0.8461917)
VALUES_SA<- c(0.26746011, 0.07625159, 0.11686592, 0.23892777, 0.30049461)
COUNT_GA<- c(150)
COUNT_SA<- c(3000)
OPTIMAL_VALUE_GA<- c(27.28861)
OPTIMAL_VALUE_SA<- c(0.07366332)
```

### Plotting Table

```{r}
data.frame(TICKER_NAMES,VALUES_GA,VALUES_SA)
data.frame(COUNT_GA,COUNT_SA,OPTIMAL_VALUE_GA,OPTIMAL_VALUE_SA)
```
