---
title: "imdb_Droupout"
output:
  html_document:
    df_print: paged
  html_notebook:
    highlight: textmate
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


## The IMDB dataset


We'll be working with "IMDB dataset", a set of 50,000 highly-polarized reviews from the Internet Movie Database. They are split into 25,000 reviews for training and 25,000 reviews for testing, each set consisting in 50% negative and 50% positive reviews.



```{r, results='hide'}
library(keras)
imdb <- dataset_imdb(num_words = 10000)
c(c(train_data, train_labels), c(test_data, test_labels)) %<-% imdb
```

```{r}
str(train_data[[1]])
```

```{r}
train_labels[[1]]
```

Since we restricted ourselves to the top 10,000 most frequent words, no word index will exceed 10,000:

```{r}
max(sapply(train_data, max))
```

For kicks, here's how you can quickly decode one of these reviews back to English words:

```{r}
# word_index is a dictionary mapping words to an integer index
word_index <- dataset_imdb_word_index()
# We reverse it, mapping integer indices to words
reverse_word_index <- names(word_index)
names(reverse_word_index) <- word_index
# We decode the review; note that our indices were offset by 3
# because 0, 1 and 2 are reserved indices for "padding", "start of sequence", and "unknown".
decoded_review <- sapply(train_data[[1]], function(index) {
  word <- if (index >= 3) reverse_word_index[[as.character(index - 3)]]
  if (!is.null(word)) word else "?"
})
```

```{r}
cat(decoded_review)  # Sample Review
```

## Preparing the data


```{r}
vectorize_sequences <- function(sequences, dimension = 10000) {
  # Create an all-zero matrix of shape (len(sequences), dimension)
  results <- matrix(0, nrow = length(sequences), ncol = dimension)
  for (i in 1:length(sequences))
    # Sets specific indices of results[i] to 1s
    results[i, sequences[[i]]] <- 1
  results
}
# Our vectorized training data
x_train <- vectorize_sequences(train_data)
# Our vectorized test data
x_test <- vectorize_sequences(test_data)
```

Here's samples final look:

```{r}
str(x_train[1,])
```

vectorizinf the labels:

```{r}
# Our vectorized labels
y_train <- as.numeric(train_labels)
y_test <- as.numeric(test_labels)
```


## Building our network

layers: `relu` activations: `layer_dense(units = 32, activation = "relu")`, layer_dropout(rate = 0.6).



```{r}
library(keras)
model <- keras_model_sequential() %>% 
  layer_dense(units = 32, activation = "relu", input_shape = c(10000)) %>% 
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 32, activation = "relu") %>% 
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 1, activation = "sigmoid")
```

Optimizer: `rmsprop` 
loss function:`binary_crossentropy` 

```{r}
model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)
```

passing an optimizer instance as the `optimizer` argument: 


```{r}
model %>% compile(
  optimizer = optimizer_rmsprop(lr=0.001),
  loss = "binary_crossentropy",
  metrics = c("accuracy")
) 
```

passing function objects as the `loss` or `metrics` arguments:

```{r}
model %>% compile(
  optimizer = optimizer_rmsprop(lr = 0.001),
  loss = loss_binary_crossentropy,
  metrics = metric_binary_accuracy
) 
```

## Validating our approach


```{r}
val_indices <- 1:10000
x_val <- x_train[val_indices,]
partial_x_train <- x_train[-val_indices,]
y_val <- y_train[val_indices]
partial_y_train <- y_train[-val_indices]
```

epochs :20 iterations over all samples in the `x_train` and `y_train` tensors
batches:512 samples. 

```{r, echo=TRUE, results='hide'}
model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)
history <- model %>% fit(
  partial_x_train,
  partial_y_train,
  epochs = 10,
  batch_size = 512,
  validation_data = list(x_val, y_val)
)
```



```{r}
str(history)
```



```{r}
plot(history)
```



```{r, echo=TRUE, results='hide'}
model <- keras_model_sequential() %>% 
  layer_dense(units = 32, activation = "relu", input_shape = c(10000)) %>% 
   layer_dropout(rate = 0.6) %>%
  layer_dense(units = 32, activation = "relu") %>% 
   layer_dropout(rate = 0.6) %>%
  layer_dense(units = 1, activation = "sigmoid")
model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)
model %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results <- model %>% evaluate(x_test, y_test)
```

```{r}
results
```
 

## Using a trained network to generate predictions on new data



```{r}
model %>% predict(x_test[1:10,])
```